---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tidyverse)
library(patchwork)
library(crgg)
```

# crgg

<!-- badges: start -->
<!-- badges: end -->

`crgg` is a package with my personal themes. I think they are really nice and possibly useful for others too.

## Installation

You can install crgg from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("reitancorp/crgg")
```

## Usage

`crgg` includes two themes, `theme_crgg_minimal()` and `theme_crgg_standard()`. They can be used like any standard `ggplot` theme:

```{r example, eval = F}
library(ggplot)
library(crgg)
...
my_ggplot + theme_crgg_standard()
```

What's the differeence between the minimal and standard themes? Lets check:

```{r fig.height=3.5}
myplot <-
  cars %>%
  ggplot(aes(x = speed, y = dist)) +
  geom_point()
p1 <- myplot + theme_crgg_minimal()
p2 <- myplot + theme_crgg_standard()
p1 + p2
```

So, as you can see, minimal has no axis lines, but standard does.

## Fonts
The themes includes the arguments `base_size` and `base_size` which controls font size and typeface. The standard is `base_size = 8` and `base_family = "Palatino"`. Note that the font needs to be installed on your computer, and fonts at least works fine on MacOS. 

```{r fig.height=3.5}
p3 <- myplot + theme_crgg_minimal(base_size = 12, base_family = "Helvetica")
p4 <- myplot + theme_crgg_standard(base_siz = 8, base_family = "Impact")
p3 + p4
```

## Color themes
The themes also includes some standard color schemes through the argument `bgcolor`. Options for `theme_crgg_minimal()` are `"white"`or  `"black"`. For `theme_crgg_standard()`, `"white"`, `"grey"`, `"offwhite"`, `"black"`

```{r }
p6 <- myplot + theme_crgg_standard(bgcolor = "white")
p7 <- myplot + theme_crgg_standard(bgcolor = "grey")
p8 <- myplot + theme_crgg_standard(bgcolor = "offwhite")
p9 <- myplot + theme_crgg_standard(bgcolor = "black")
(p6 + p7) / (p8 + p9)
```



## Horizontal lines
Use `horizontal = TRUE`for horizontal lines. 
```{r }
myplot + theme_crgg_standard(horizontal = T)
```


# KI color palettes

Because I am affiliated with KI I sometimes have to use their official graphic profile. 

NOTE: For the full KI experience, you should use the above themes with `base_family = "DM Sans"`. Note that DM Sans must be installed, but hey, it's free. Downoad it at [https://fonts.google.com/specimen/DM+Sans](https://fonts.google.com/specimen/DM+Sans).

The package includes the color palette functions `scale_fill_ki_d()`, `scale_fill_ki_c()`, `scale_color_ki_d()` and `scale_color_ki_()`. The palettes are defined in HEX colors from https://medarbetare.ki.se/farger-i-kis-grafiska-profil. It includes four palettes which can be ordered in different ways (`order = c("original", "gradient", "hue")`). Use whichever order you like, but if you have continuous variables, the `"gradient"` option (default) might serve you best.  

Let's have a look:

```{r}
barplot5 <-
  mtcars %>%
  arrange(desc(disp)) %>%
  filter(row_number() %in% 1:5) %>%
  rownames_to_column() %>%
  ggplot(aes(x = rowname, y = mpg, fill = rowname)) +
  geom_col()
p10 <-
  barplot5 + 
  scale_fill_ki_d(palettename = "ki_primary")
barplot <-
  mtcars %>%
  arrange(desc(disp)) %>%
  filter(row_number() %in% 1:6) %>%
  rownames_to_column() %>%
  ggplot(aes(x = rowname, y = mpg, fill = rowname)) +
  geom_col()
p11 <- barplot +
  scale_fill_ki_d(palettename = "ki_function_1")
p12 <- barplot+
  scale_fill_ki_d(palettename = "ki_function_2")
p13 <- barplot +
  scale_fill_ki_d(palettename = "ki_function_3")
(p10 + p11) / (p12 + p13)
```

Note that `ki_primary` only contains 5 colors. 


## Putting it all together

Lets make a nice graph:

```{r}
mtcars %>%
   ggplot(aes(x= mpg, y = disp, color = factor(cyl))) +
  geom_point() +
  facet_wrap(~ case_when(gear == 3 ~ "3 gears",gear == 4 ~ "4 gears",gear == 5 ~ "5 gears")) +
  theme_crgg_standard(base_family = "DM Sans", horizontal = T) +
  scale_colour_ki_d(palettename = "ki_function_1", order = "hue") +
  ylab("Displacement") + xlab("Miles per gallon") +
  labs(color = "No. of cylinders",
       caption = "Well formulated caption",
       tag = "A",
       title = "Compelling title")
```

